Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-18 Cover_letter_JPM.tex
Updates from Overleaf

Enclosed, please find our revised manuscript (jpm-1174473) entitled "Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Journal of Personalized Medicine. We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.

@@

We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
%=> defense: 
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來(like Figure 4: (Please see supplementary Figure SXXX))
%說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
% file: 1453 Feb 15 2020 ./intermediate_data/HNSCC_OS_marginSFP_pvalueBonferroni_KM_candidate_cox.Rda => candidate_sample
%[1] "HNSCC_OS_marginS_pvalueBonferroni_sorted"   
%[2] "HNSCC_OS_marginFree_pvalueBonferroni_sorted"
%[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs at 50\% or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4").
Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a p-value of \num{1e-6} at 70\% quantile cutoff. After the FDR correction, NDFIP1 still has \textit{P} value of \num[3]{0.0001074233}.
%Rplot_pvaluePlot_NDFIP1.pdf
%  to find cases_OS outside of range 180-220 (== cutoff not at median)
%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
%# NDFIP1 (within our 20 preliminary candidates), 
In the \textit{P} value plot (Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
supplementary figure ??), we could see a sliding-window selection with cutoff finding might collect more candidate (\textit{P} $<0.05$) for further Cox's modeling.
%Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
Indeed, it needs to be validated by the other independent cohort.

% and a new Figure 4
\begin{figure}[hp]

@@

% supplementary figure
\begin{figure}[ht]
    \centering
    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} value is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
    (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
    \label{fig:pvaluePlot_NDFIP1}
\end{figure}

%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
Thus we performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.

%\begin{MyColorPar}{red}
%\end{MyColorPar}

% and FDR (done; ok)
We also modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
%Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} has been be applied and shows which genes should be retained for further univariate and multivariate analysis.
% of Cox modeling
It is ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
\end{MyColorPar}

@@

%

\subsection*{2-2}
%(OK)
I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone

%
\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comment.
We changed title as "Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
There is more evidence to validate them (please see Answer 2-3).

>>>>

Enclosed, please find our revised manuscript (jpm-1174473) entitled "Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Journal of Personalized Medicine. We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.

@@

We also think that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
%=> defense: 
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來(like Figure 4: (Please see supplementary Figure SXXX))
%說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
% file: 1453 Feb 15 2020 ./intermediate_data/HNSCC_OS_marginSFP_pvalueBonferroni_KM_candidate_cox.Rda => candidate_sample
%[1] "HNSCC_OS_marginS_pvalueBonferroni_sorted"   
%[2] "HNSCC_OS_marginFree_pvalueBonferroni_sorted"
%[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).
Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
supplementary figure S1). After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233}.
%Rplot_pvaluePlot_NDFIP1.pdf
%  to find cases_OS outside of range 180-220 (== cutoff not at median)
%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
%# NDFIP1 (within our 20 preliminary candidates), 
In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more potential candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
%Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
Indeed, it needs to be validated by the other independent cohort.

% and a new Figure 4
\begin{figure}[ht]

@@

% supplementary figure
\begin{figure}[ht]
    \centering
    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} values is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
    (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
    \label{fig:pvaluePlot_NDFIP1}
\end{figure}

%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
We performed the FDR correction applied on the Kaplan-Meier \textit{P} values of cutoff finding procedure, then Bonferroni adjustment of those \textit{P} values for candidate selection.
%\begin{MyColorPar}{red}
%\end{MyColorPar}
% and FDR (done; ok)
We modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
%Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
%***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} has been be applied and shows which genes should be retained for further univariate and multivariate analysis.
% of Cox modeling
It is ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
Then Bonferroni adjustment of those \textit{P} values has been used for candidate selection.
\end{MyColorPar}

@@

%
\clearpage
\subsection*{2-2}
%(OK)
I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone

%
\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comment.
We changed title as "Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
There is more evidence to validate them (please see Answer 2-3).

### 2021-06-18 Supplementary_figures.tex
Updates from Overleaf

\begin{document}
%%%%%%%%% title
% Full title of the paper (Capitalized)
%\Title{
x Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
%}

@@

\begin{table}

@@

\begin{table}[hp]

@@

\section{SFigures}
\underline{Supplementary figure legends}\\[1cm]
%S1
Supplementary Figure \ref{fig:fig_GSE2837}\\
GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

% x S2
Supplementary Figure \ref{fig:fig_SurvExpress}\\
The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low.
Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.

%x S3
Supplementary Figure \ref{fig:fig_HPA_USP10}\\
The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
Over-expression of USP10 has poor prognosis on HNSCC.

%%%%%
% S1
% from Answer2-2 GSE2837; 
\begin{figure}
\raggedleft
\includegraphics[width=12cm]{Answer_2-2.pdf}
\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
\label{fig:fig_GSE2837}
\end{figure}

% SFigure 2, SurvExpress
% red or green is NOT by expression level
\begin{figure}
\raggedleft
\includegraphics[width=10cm]{Answer_3-1.pdf}
\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
\label{fig:fig_SurvExpress}
\end{figure}
\clearpage

%%
% S3
\begin{figure}
\raggedleft
\includegraphics[width=12cm]{Answer_3-1_USP10.pdf}
\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
Overexpression of USP10 has poor prognosis on HNSCC.}
\label{fig:fig_HPA_USP10}
\end{figure}
%\clearpage

@@

>>>>

\begin{document}
%%%%%%%%% title
% Full title of the paper (Capitalized)
\Title{Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}\\[2cm]
%x Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
%}

@@

\begin{table}[ht]

@@

\begin{table}[ht]

@@

\clearpage

%%%%%%%%%%%%

\section{SFigures}
\underline{Supplementary figure legends}\\[1cm]
%S1
Supplementary figure \ref{fig:pvaluePlot_NDFIP1}\\
The gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see supplementary Figure S1). After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233}.
However, NDFIP1 could not pass the validation by using GSE65858 cohort.

%S2
Supplementary Figure \ref{fig:fig_GSE2837}\\
GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

% x S2
%Supplementary Figure \ref{fig:fig_SurvExpress}\\
%The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
%Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low. Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.

% x S3
%Supplementary Figure \ref{fig:fig_HPA_USP10}\\
%The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018). Over-expression of USP10 has poor prognosis on HNSCC.

%%%%%
% S1
% supplementary figure
\begin{figure}[ht]
    \centering
    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} values is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
    (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
    \label{fig:pvaluePlot_NDFIP1}
\end{figure}

% S2
% from Answer2-2 GSE2837; 
\begin{figure}
\raggedleft
\includegraphics[width=12cm]{Answer_2-2.pdf}
\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
\label{fig:fig_GSE2837}
\end{figure}

@@

% x SFigure 2, SurvExpress
% red or green is NOT by expression level
\begin{figure}
\raggedleft
\includegraphics[width=10cm]{Answer_3-1.pdf}
\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
\label{fig:fig_SurvExpress}
\end{figure}
\clearpage

%%
%x S3
\begin{figure}
\raggedleft
\includegraphics[width=12cm]{Answer_3-1_USP10.pdf}
\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
Overexpression of USP10 has poor prognosis on HNSCC.}
\label{fig:fig_HPA_USP10}
\end{figure}
%\clearpage

### 2021-06-18 main.tex
Updates from Overleaf

%=================================================================
% Full title of the paper (Capitalized)
\Title{Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
%\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
%\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
%\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
%\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
